
\documentclass[11pt,a4paper,oneside]{book}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{fancyhdr}
\usepackage{enumitem}

% Custom Colors for the Shokunin Aesthetic
\definecolor{shokunin_blue}{RGB}{0, 51, 102}
\definecolor{terminal_green}{RGB}{0, 200, 0}
\definecolor{amber}{RGB}{255, 191, 0}
\definecolor{code_bg}{RGB}{248, 248, 248}

% Code Block Styling
\lstset{
    backgroundcolor=\color{code_bg},
    basicstyle=\ttfamily\small,
    breaklines=true,
    commentstyle=\color{gray},
    keywordstyle=\color{shokunin_blue},
    stringstyle=\color{orange},
    frame=single,
    rulecolor=\color{gray!30}
}

% Heading Styles
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries\color{shokunin_blue}}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titleformat{\section}
  {\normalfont\Large\bfseries\color{shokunin_blue}}{\thesection}{1em}{}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{The Shokunin AI Holy Bible}
\fancyhead[R]{Local Scope | Sovereign Operator}
\fancyfoot[C]{\thepage}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge \textbf{THE SHOKUNIN HOLY BIBLE} \par}
    \vspace{0.5cm}
    {\Large \textbf{The Holy Grail of AI-Assisted Development} \par}
    \vspace{2cm}
    {\large \textit{A Comprehensive Codification of the Aider-Gemini Protocol} \par}
    \vspace{1cm}
    {\large \textbf{Phase: The Extraction} \par}
    \vspace{4cm}
    \begin{tcolorbox}[colback=shokunin_blue!5,colframe=shokunin_blue,title=System Directives]
        1. Protect the Air-Gap \\
        2. Minimize Cognitive Entropy \\
        3. Maintain Local Sovereignty \\
        4. Execute with Surgical Precision
    \end{tcolorbox}
    \vfill
    {\large v1.0 | April 2026 \par}
\end{titlepage}

\tableofcontents

\chapter{The Genesis: Strategic Laziness}
\section{The Philosophy of the Single Blade}
The "Brain Fry" observed in the masses stems from managing multiple autonomous agents. For the Shokunin, we reject the circus of multi-agent orchestration in favor of the \textbf{Single Blade Principle}. We use one high-performance model (GPT-5.3 or Gemini 2.0 Pro) within a controlled environment. Strategic laziness is the art of doing the thinking once (The Spec) so the machine can do the heavy lifting a thousand times (The Implementation).

\section{The ADHD Guardrails}
In deep focus, every context switch is a high-cost tax. We use AI not to replace our focus, but to handle the "Lateral Noise"—the boilerplate, the unit tests, and the repetitive refactoring that causes focus to leak.

\chapter{The Architect: Gemini CLI Deep Dive}
\section{Synthesizing the Truth}
Gemini CLI is the "Master Secretary." Its primary role is not code generation, but \textbf{System Mapping} and \textbf{Spec Synthesis}. 
\begin{itemize}
    \item \textbf{High Context Mapping:} Use Gemini to ingest your entire project and output a markdown status report of all technical debt.
    \item \textbf{Blueprint Creation:} Before opening Aider, use Gemini CLI to draft your feature specs. This creates a "Logical Air-Gap."
\end{itemize}

\section{The Spec-Writing Prompt Engineering}
To generate specs like the Dual Filter LFO Matrix, use a recursive prompt:
\begin{lstlisting}[language=bash]
# The Gemini CLI Shokunin Prompt
gemini-cli "Analyze the current /src/audio_engine and draft a feature specification for a Dual Filter LFO Matrix. Include source-to-destination mappings, mathematical scaling for 'Drive' parameters, and ensure congruence with the existing HMA 34 filter logic. Output to /doc/features/."
\end{lstlisting}

\section{Information Distillation}
Use Gemini CLI to summarize 200-page Azure API documentation into a single \texttt{context.md} file. This file becomes the "Source of Truth" that you will later feed to Aider via \texttt{/read}.

\chapter{The Surgeon: Aider Technical Mastery}
\section{The Core Command Set}
Aider is the hammer. You must know your tools by feel.
\begin{itemize}
    \item \textbf{/read:} Mounts a file as read-only. Use this for your "Constitution" and specs.
    \item \textbf{/add:} Mounts a file for surgery. Only add the files you are currently cutting.
    \item \textbf{/ask:} The "Consultant" mode. This generates code in the chat but never touches the disk. This is the ultimate tool for the "Ask and Pick" workflow.
    \item \textbf{/map-tokens:} Control the visibility of your repo. On high-complexity Azure refactors, set to \texttt{4096}.
\end{itemize}

\section{Architect Mode vs. Code Mode}
\textbf{Architect Mode} (\texttt{--architect}) is the 2026 standard for high-stakes engineering.
\begin{enumerate}
    \item \textbf{The Proposal:} The model explains the plan.
    \item \textbf{The Review:} You verify the logic (The Shokunin Gate).
    \item \textbf{The Application:} Aider applies the diff with surgical precision.
\end{enumerate}

\section{The .aider.history Archive}
Treat the history file as your "Code Warehouse." When Aider hallucinates a YAML edit, do not let it try again on the same file. Use \texttt{/undo}, then go to \texttt{.aider.history}, copy the clean code snippet, and place it manually. This is the "Manual Air-Gap."

\chapter{The Doctrine of Integration}
\section{Integrating Music (MPC) and Code}
The Shokunin sees no difference between a Modulation Matrix in a synth and a Bias Filter (HMA 34) in a trading bot. We use Aider to build scripts that bridge these worlds—specifically using Python to map MIDI data from the MPC into JSON structures for AI search skillsets.

\section{The Trading/Coding Symbiosis}
Use Aider to automate the "Extraction" of trading logs.
\begin{lstlisting}[language=bash]
# Aider Analysis Command
aider --model gpt-5.3 --msg "Analyze my last 50 trades from logs/trades.csv. Identify where price was below HMA 34 but I remained in a long position. Write a report on 'Danger Zone' violations."
\end{lstlisting}

\chapter{The Fortress: Hardware Sovereignty}
\section{The 3090/Gemma 4 Configuration}
Running Gemma 4 locally on 24GB VRAM allows for \textbf{Test-Time Scaling}. You can set a local script to let Gemma 4 "Think" about a complex LFO modulation bug for 30 minutes, testing 100 variations in a local container until it finds the mathematically perfect solution.

\section{The Power of Local LLM Caching}
By using local models, you cache your specific coding style. Over time, the local model learns your "Local Scope" (your preference for clean YAML, your specific Azure deployment patterns) without ever leaking that data to the cloud.

\chapter{The Holy Grail Workflow}
\section{The 7-Step Shokunin Protocol}
\begin{enumerate}
    \item \textbf{Observe:} Identify a need (Trading indicator, Music script, AI Skillset).
    \item \textbf{Architect:} Use Gemini CLI to write the \texttt{doc/spec.md}.
    \item \textbf{Isolate:} Launch Aider and \texttt{/read} the spec.
    \item \textbf{Draft:} Use \texttt{/ask} to see the proposed logic.
    \item \textbf{Execute:} Use \texttt{--architect} to apply the core logic.
    \item \textbf{Verify:} Run local tests using \texttt{/run}.
    \item \textbf{Sovereignty:} Commit the win and close the screen. Return to the Fortress.
\end{enumerate}

\section{The End of the Auction}
We no longer bid our time against the chaos of the world. We have extracted our hardware, built our fortress, and codified our excellence. The AI does not replace us; it serves the Sovereign Operator.

\end{document}
